---
title: "RNAseq from human tissues 2026"
subtitle: "Different tissues, 205 samples"
author: "Sulev Koks"
date: "05/07/2026"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Tissue GTEx expression

```{r}
setwd("/Users/sulevkoks/Documents/R_Data/GTEx")
wd<-("/Users/sulevkoks/Documents/R_Data/GTEx")
```

```{r}
library(readxl)
GTExTissues <- read_excel("GTExTissues.xlsx")
View(GTExTissues)
```

```{r}
library(readxl)
xlsxfile <- file.path(wd,"GTExTissues.xlsx")
sampleTable <- read_excel(xlsxfile)
View(sampleTable)

table(sampleTable$sampleID)
dfsamples<-data.frame(sampleTable)
str(dfsamples)
table(dfsamples$sampleID, dfsamples$tissue)
table(dfsamples$tissue)
table(dfsamples$subject)
```

```{r}
dim(sampleTable)
```

#RNA-Seq workflow
This workflow is based on quant files from Salmon

```{r}
library(tximeta)
library(DESeq2)
library(GenomicRanges)
library(GenomicFeatures)
```

We define work directory where we have the data:

```{r}
dir<-("/Users/sulevkoks/Documents/R_Data/tissueRNAseq")
```

```{r}
samples <- data.frame(sampleTable)
samples
files <- file.path(dir, "tissue205quant",samples$sampleID, "quant.sf")
files
all(file.exists(files))
```

```{r}
coldata <- data.frame(files, names=samples$sampleID, samples)
```

```{r}
se <- tximeta(coldata)
```

```{r}
colData(se)
colnames(se)
```

```{r gtf}
gtffile <- ("gencode.v49.chr_patch_hapl_scaff.annotation.gtf")
```

```{r}
(txdb <- txdbmaker::makeTxDbFromGFF(gtffile, format="gtf"))
head(seqlevels(txdb))
```

```{r}
assayNames(se)
```

```{r}
rowRanges(se)
```

```{r}
seqinfo(se)
```

```{r exons}
se.exons <- addExons(se)
rowRanges(se.exons)[[1]]
```

```{r}
save(se,file = "SEtissuesRNAseqTX.RData")
```

Gene-level summarisation

```{r gene level}
gse <- summarizeToGene(se)
rowRanges(gse)
```

```{r}
dim(se)
dim(gse)
```

```{r}
load("ddsGTExtissues.RData")
```

DESeq2

```{r}
suppressPackageStartupMessages(library(DESeq2))
gse$tissue
gse$subject
gse$tissue <- factor(gse$tissue)
gse$subject <- factor(gse$subject)
gse$tissue
gse$subject
colData(gse)
```

this didn't work
```{r}
colData(gse)[8:39] <- sapply(colData(gse)[8:39],as.factor)
```

```{r}
gse$adipose <- factor(gse$adipose)
gse$adrenal  <- factor(gse$adrenal)
gse$appendix <- factor(gse$appendix)
gse$bladder <- factor(gse$bladder)
gse$bonemarrow <- factor(gse$bonemarrow)
gse$cerebralcortex <- factor(gse$cerebralcortex)
gse$colon <- factor(gse$colon)
gse$duodenum <- factor(gse$duodenum)
gse$endometrium <- factor(gse$endometrium)
gse$esophagus <- factor(gse$esophagus)
gse$fallopiantube <- factor(gse$fallopiantube)
gse$gallbladder <- factor(gse$gallbladder)
gse$heart <- factor(gse$heart)
gse$kidney <- factor(gse$kidney)
gse$liver <- factor(gse$liver)
gse$lung <- factor(gse$lung)
gse$lymphnode <- factor(gse$lymphnode)
gse$ovary <- factor(gse$ovary)
gse$pancreas <- factor(gse$pancreas)
gse$placenta <- factor(gse$placenta)
gse$prostate <- factor(gse$prostate)
gse$rectum <- factor(gse$rectum)
gse$salivarygland <- factor(gse$salivarygland)
gse$skeletalmuscle <- factor(gse$skeletalmuscle)
gse$skin <- factor(gse$skin)
gse$smallintestine <- factor(se$smallintestine)
gse$smoothmuscle <- factor(gse$smoothmuscle)
gse$spleen <- factor(gse$spleen)
gse$stomach <- factor(se$stomach)
gse$testis <- factor(gse$testis)
gse$thyroid <- factor(gse$thyroid)
gse$tonsil <- factor(gse$tonsil)
```

```{r}
save(gse, file="gSEtissuesRNAseqGE.RData")
```
```{r}
load("gSEtissuesRNAseqGE.RData")
```

```{r}
#gse[sapply(gse, is.character)] <- lapply(gse[sapply(gse, is.character)], as.factor)
```

##Prepare ENSEMBL annotation to the res tables.

```{r}
#BiocManager::install("biomaRt")
library(biomaRt)
```

```{r}
listMarts()
ensembl_hs_mart <- useMart(biomart="ensembl", dataset="hsapiens_gene_ensembl") 
ensembl_df <- getBM(attributes=c("ensembl_gene_id","description","ensembl_transcript_id","hgnc_symbol", "entrezgene_trans_name","chromosome_name", "band", "entrezgene_id", "external_transcript_name"), mart=ensembl_hs_mart)
```

## April 2024
#### GENE level analysis
Also January 2026 and July 2026

```{r tissue}
gdds <- DESeqDataSet(gse, design = ~ tissue)
```

```{r}
colData(gse)
colnames(colData(gse))
```

From a `gdds` object.
gddsAD <- DESeqDataSet(gdds, design = ~ adipose)

```{r GENE level}
gddsAD <- DESeqDataSet(gdds, design = ~ adipose)
gddsADR <- DESeqDataSet(gdds, design = ~ adrenal)

gddsAPP <- DESeqDataSet(gdds, design = ~ appendix)
gddsBLDDR <- DESeqDataSet(gdds, design = ~ bladder)

gddsBM <- DESeqDataSet(gdds, design = ~bonemarrow)
gddsCRTX <- DESeqDataSet(gdds, design = ~cerebralcortex)
gddsCOL <- DESeqDataSet(gdds, design = ~colon)
gddsDUO <- DESeqDataSet(gdds, design = ~duodenum)
gddsENDO <- DESeqDataSet(gdds, design = ~endometrium)
gddsESO <- DESeqDataSet(gdds, design = ~esophagus)
gddsFALL <- DESeqDataSet(gdds, design = ~fallopiantube)
gddsGALL <- DESeqDataSet(gdds, design = ~gallbladder)
gddsHEART <- DESeqDataSet(gdds, design = ~heart)
gddsKIDN <- DESeqDataSet(gdds, design = ~kidney)
gddsLIV <- DESeqDataSet(gdds, design = ~liver)
gddsLUNG <- DESeqDataSet(gdds, design = ~lung)
gddsLYMN <- DESeqDataSet(gdds, design = ~lymphnode)
gddsOVARY <- DESeqDataSet(gdds, design = ~ ovary)
gddsPAN <- DESeqDataSet(gdds, design = ~pancreas)
gddsPLAC <- DESeqDataSet(gdds, design = ~placenta)
gddsPROS <- DESeqDataSet(gdds, design = ~prostate)
gddsREC <- DESeqDataSet(gdds, design = ~rectum)

gddsSALG <- DESeqDataSet(gdds, design = ~salivarygland)
gddsSKEL <- DESeqDataSet(gdds, design = ~skeletalmuscle)

gddsSKIN <- DESeqDataSet(gdds, design = ~skin)
gddsSMINT <- DESeqDataSet(gdds, design = ~smallintestine)
gddsSMOO <- DESeqDataSet(gdds, design = ~smoothmuscle)
gddsSPLEEN <- DESeqDataSet(gdds, design = ~spleen)
gddsSTOMACH <- DESeqDataSet(gdds, design = ~stomach)
gddsTEST <- DESeqDataSet(gdds, design = ~testis)
gddsTHYR <- DESeqDataSet(gdds, design = ~thyroid)
gddsTON <- DESeqDataSet(gdds, design = ~tonsil)
```

```{r}
gdds <- DESeq(gdds)
```

```{r}
gddsAD <- DESeq(gddsAD)
gddsADR <- DESeq(gddsADR)
gddsAPP <- DESeq(gddsAPP)
gddsBLDDR <- DESeq(gddsBLDDR)
```

```{r}
gddsBM <- DESeq(gddsBM)
gddsCRTX <- DESeq(gddsCRTX)
gddsCOL <- DESeq(gddsCOL)
gddsDUO <- DESeq(gddsDUO)
gddsENDO <- DESeq(gddsENDO)
gddsESO <- DESeq(gddsESO)
gddsFALL <- DESeq(gddsFALL)
gddsGALL <- DESeq(gddsGALL)
gddsHEART <- DESeq(gddsHEART)
gddsKIDN <- DESeq(gddsKIDN)
gddsLIV <- DESeq(gddsLIV)
gddsLUNG <- DESeq(gddsLUNG)
gddsLYMN <- DESeq(gddsLYMN)
gddsOVARY <- DESeq(gddsOVARY)
gddsPAN <- DESeq(gddsPAN)
gddsPLAC <- DESeq(gddsPLAC)
gddsPROS <- DESeq(gddsPROS)
gddsREC <- DESeq(gddsREC)

gddsSALG <- DESeq(gddsSALG)
gddsSKEL <- DESeq(gddsSKEL)

gddsSKIN <- DESeq(gddsSKIN)
gddsSMINT <- DESeq(gddsSMINT)
gddsSMOO <- DESeq(gddsSMOO)

gddsSPLEEN <- DESeq(gddsSPLEEN)
gddsSTOMACH <- DESeq(gddsSTOMACH)
gddsTEST <- DESeq(gddsTEST)
gddsTHYR <- DESeq(gddsTHYR)
gddsTON <- DESeq(gddsTON)
```

```{r}
save(gdds, file="gDDS_SEtissuesRNAseqGE.RData")
```

```{r}
normcodata<-counts(gdds, normalized=T)
write.table(as.data.frame(normcodata), file="NormCountdata_205Tissues.txt", sep="\t")
```

```{r}
(res <- results(gdds,  alpha=0.05))
summary(res)
```

```{r}
(resAD <- results(gddsAD,  alpha=0.05))
summary(resAD)
(resOrderedAD <- resAD[order(resAD$padj),])
(resADR <- results(gddsADR,  alpha=0.05))
summary(resADR)
(resAPP <- results(gddsAPP,  alpha=0.05))
summary(resAPP)
(resBLDR <- results(gddsBLDDR,  alpha=0.05))
summary(resBLDR)
(resBM <- results(gddsBM,  alpha=0.05))
summary(resBM)
(resCRTX <- results(gddsCRTX,  alpha=0.05))
summary(resCRTX)
(resCOL <- results(gddsCOL,  alpha=0.05))
summary(resCOL)
(resDUO <- results(gddsDUO,  alpha=0.05))
summary(resDUO)
(resENDO <- results(gddsENDO,  alpha=0.05))
summary(resENDO)
(resESO <- results(gddsESO,  alpha=0.05))
summary(resESO)
(resFALL <- results(gddsFALL,  alpha=0.05))
summary(resFALL)
(resGALL <- results(gddsGALL,  alpha=0.05))
summary(resGALL)
(resHEART <- results(gddsHEART,  alpha=0.05))
summary(resHEART)
(resKIDN <- results(gddsKIDN,  alpha=0.05))
summary(resKIDN)
```

```{r}
(resLIV <- results(gddsLIV,  alpha=0.05))
summary(resLIV)
(resLUNG <- results(gddsLUNG,  alpha=0.05))
summary(resLUNG)
(resLYMN <- results(gddsLYMN,  alpha=0.05))
summary(resLYMN)
(resOV <- results(gddsOVARY,  alpha=0.05))
summary(resOV)
(resPAN <- results(gddsPAN,  alpha=0.05))
summary(resPAN)
(resPLAC <- results(gddsPLAC,  alpha=0.05))
summary(resPLAC)
(resPROS <- results(gddsPROS,  alpha=0.05))
summary(resPROS)
(resREC <- results(gddsREC,  alpha=0.05))
summary(resREC)
(resSALG <- results(gddsSALG,  alpha=0.05))
summary(resSALG)
```

```{r}
(resSKEL <- results(gddsSKEL,  alpha=0.05))
summary(resSKEL)
(resSKIN <- results(gddsSKIN,  alpha=0.05))
summary(resSKIN)
(resSMINT <- results(gddsSMINT,  alpha=0.05))
summary(resSMINT)
(resSMOO <- results(gddsSMOO,  alpha=0.05))
summary(resSMOO)
(resSPLEEN <- results(gddsSPLEEN,  alpha=0.05))
summary(resSPLEEN)
(resSTOMACH <- results(gddsSTOMACH,  alpha=0.05))
summary(resSTOMACH)
(resTEST <- results(gddsTEST,  alpha=0.05))
summary(resTEST)
(resTHYR <- results(gddsTHYR,  alpha=0.05))
summary(resTHYR)
(resTON <- results(gddsTON,  alpha=0.05))
summary(resTON)
```

Annotation for `resOrdered` object using BIOMART.

```{r}
res <- resAD
res <- resADR
res <- resAPP
res <- resBLDR
res <- resBM
res <- resCRTX
res <- resCOL
res <- resDUO
res <- resENDO
res <- resESO
res <- resFALL
res <- resGALL
res <- resHEART
res <- resKIDN
res <- resLIV
res <- resLUNG
res <- resLYMN
res <- resOV
res <- resPAN
res <- resPLAC
res <- resPROS
res <- resREC
res <- resSALG
```

```{r}
res <- resSKEL
res <- resSKIN
res <- resSMINT
res <- resSMOO
res <- resSPLEEN
res <- resSTOMACH
res <- resTEST
res <- resTHYR
res <- resTON
```

```{r adjust rownames}
rownames(res)
row.names(res)[1:10]
res$GENE<-row.names(res)
rownames(res)<- gsub("\\..*", "", res$GENE)
rownames(res)[1:10]
resOrdered <- res[order(res$padj),]
head(resOrdered)
```

```{r}
my_genes = row.names(resOrdered)
my_genes_ann = ensembl_df[match(my_genes, ensembl_df$ensembl_gene_id),]
colnames(my_genes_ann)
my_genes_ann
```

```{r}
res2 <- cbind(resOrdered, my_genes_ann[match(rownames(resOrdered), my_genes_ann$ensembl_gene_id), ,drop=FALSE])
resOrdered <- res2[order(res2$padj),]
resSig <- subset(resOrdered, padj < 0.05)
head(resSig)
```

```{r}
write.csv(as.data.frame(resSig), file="resSigADIPOSEFDR005.csv")
write.csv(as.data.frame(resSig), file="resSigADRENALFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigAPPENDIXFDR005.csv")
write.csv(as.data.frame(resSig), file="resSigBLADDERFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigBONEMARROWFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigCEREBRALCORTEXFDR005.csv")
write.csv(as.data.frame(resSig), file="resSigCOLONFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigDUODENUMFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigENDOMETRIUMFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigESOPHAGUSFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigFALLOPIANTUBEFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigGALLBLADDERFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigHEARTFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigKIDNEYFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigLIVERFDR005.csv")
```

```{r}
write.csv(as.data.frame(resSig), file="resSigLUNGFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigLYMPHNODEFDR005.csv")
write.csv(as.data.frame(resSig), file="resSigOVARYFDR005.csv")
write.csv(as.data.frame(resSig), file="resSigPANCREASFDR005.csv")

```

```{r}
write.csv(as.data.frame(resSig), file="resSigPLACENTAFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigPROSTATEFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigRECTUMFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigSALIVARYGLANDFDR005.csv")

```

```{r}
write.csv(as.data.frame(resSig), file="resSigSKELETALMUSCLEFDR005.csv")
write.csv(as.data.frame(resSig), file="resSigSKINFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigSMALLINTESTINEFDR005.csv")
write.csv(as.data.frame(resSig), file="resSigSMOOTHMUSCLEFDR005.csv")
```

```{r}
write.csv(as.data.frame(resSig), file="resSigSPLEENFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigSTOMACHFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigTESTISFDR005.csv")

write.csv(as.data.frame(resSig), file="resSigTHYROIDFDR005.csv")
write.csv(as.data.frame(resSig), file="resSigTONSILFDR005.csv")
```

##Add ENSEMBL annotation to the res tables.

```{r}
#BiocManager::install("biomaRt")
library(biomaRt)
```

```{r}
listMarts()
ensembl_hs_mart <- useMart(biomart="ensembl", dataset="hsapiens_gene_ensembl") 
ensembl_df <- getBM(attributes=c("ensembl_gene_id","description","ensembl_transcript_id","hgnc_symbol", "entrezgene_trans_name","chromosome_name", "band", "entrezgene_id", "external_transcript_name"), mart=ensembl_hs_mart)
```

```{r}
res$geneID <- row.names(res)
row.names(gdds)[1:5]
rowData(gdds)$gene_id[1:5]
res$geneID <- gsub("\\..*", "", res$geneID)
rowData(gdds)$gene_id <- gsub("\\..*", "", rowData(gdds)$gene_id)
rowData(gdds)$gene_id[1:5]
my_genes = res$geneID
my_genes = rowData(gdds)$geneID

my_genes = rowData(gdds)$gene_id

my_genes_ann = ensembl_df[match(my_genes, ensembl_df$ensembl_gene_id),]
colnames(my_genes_ann)
head(my_genes_ann)
```

Annotate `res` to become `res2`

```{r res2}
res2 <- cbind(res, my_genes_ann[match(res$geneID, my_genes_ann$ensembl_gene_id), ,drop=FALSE])

resOrdered <- res2[order(res2$padj),]
resSig <- subset(resOrdered, padj < 0.05)
write.csv(as.data.frame(resSig), file="Tissue205FDR005salmon.csv")
write.csv(as.data.frame(resOrdered), file="Tissue205SalmonresOrdered.csv")
```

```{r res2}
gdds2 <- gdds
rowData(gdds2) <- cbind(rowData(gdds), my_genes_ann[match(rowData(gdds)$gene_id, my_genes_ann$ensembl_gene_id), ,drop=FALSE])
rownames(gdds2)[1:4]
rownames(gdds2)<-rowData(gdds2)$hgnc_symbol
rownames(gdds2)[1:4]

resOrdered <- res2[order(res2$padj),]
resSig <- subset(resOrdered, padj < 0.05)

write.csv(as.data.frame(resSig), file="Tissue250deseq2ensembl.csv")
write.csv(as.data.frame(resOrdered), file="Tissue250deseq2ensemblresOrdered.csv")
```

```{r}
save(gdds2, file="gDDS2_SEtissuesRNAseqGE.RData")
```

```{r}
normcodata<-counts(gdds2, normalized=T)
write.table(as.data.frame(normcodata), file="NormCountdata_250TissuesGeneId.txt", sep="\t")
```

```{r}
resSig
```

```{r}
save(resOrdered,file = "resOrdereddds_deseq205tissues.RData")
```
```{r}
save(resSig,file = "resSigdds_deseq205.RData")
```


```{r}
write.csv(res2, file="205tissuesrnaseqALL.csv")
```

## Plot counts
It can also be useful to examine the counts of reads for a single gene across the groups. A simple function for making this plot is plotCounts, which normalizes counts by the estimated size factors (or normalization factors if these were used) and adds a pseudocount of 1/2 to allow for log scale plotting. The counts are grouped by the variables in intgroup, where more than one variable can be specified. Here we specify the gene which had the smallest p value from the results table created above. You can select the gene to plot by `rowname` or by numeric index.

```{r}
dds <- gdds
dds2 <- gdds2
```


```{r}
plotCounts(dds, gene=which.min(res$padj), intgroup="tissue")
```

ENSG00000115459.18, ELMOD3
LINCADL
LEP
ADIPOQ
PLIN1
LIPE
DEFB132
PLIN4
CSN1S1
ADIPOQ-AS1

```{r ELMOD3}
plotCounts(gdds2, gene="CSN1S1", intgroup="tissue")
```

```{r ENSG00000115459.18}
plotCounts(dds, gene="ENSG00000115459.18", intgroup="tissue")
```

ENSG00000231852.9, CYP21A2

```{r ENSG00000231852.9}
plotCounts(dds, gene="ENSG00000231852.9", intgroup="tissue")
```
```{r CYP21A2}
plotCounts(dds2, gene="CYP21A2", intgroup="tissue")
```

ENSG00000145335.17, SNCA

```{r ENSG00000145335.17}
plotCounts(dds, gene="ENSG00000145335.17", intgroup="tissue")
plotCounts(dds2, gene="SNCA", intgroup="tissue")
```

MBP, cortex

```{r MBP}
plotCounts(dds2, gene="MBP", intgroup="tissue")
```

INSL5, colon

```{r INSL5}
plotCounts(dds2, gene="INSL5", intgroup="tissue")
```

CTRB2, pancreas
CTRB2
PNLIP
CELA3A

```{r CTRB2}
plotCounts(dds2, gene="CTRB2", intgroup="tissue")
```

PRTN3, bone marrow

```{r PRTN3}
plotCounts(dds2, gene="PRTN3", intgroup="tissue")
```

S100G, duodenum

```{r S100G}
plotCounts(dds2, gene="S100G", intgroup="tissue")
```

Endometrium
LINC01541
MMP10
MMP26

```{r LINC01541}
plotCounts(dds2, gene="LINC01541", intgroup="tissue")
```

TMPRSS11B

```{r TMPRSS11B}
plotCounts(dds2, gene="TMPRSS11B", intgroup="tissue")
```

Gall bladder
APCS

```{r APCS}
plotCounts(dds2, gene="APCS", intgroup="tissue")
```

Heart
NPPB
MYL7
NPPA
MYH6
TNNI3
MYBPC3

```{r NPPB}
plotCounts(gdds2, gene="MYBPC3", intgroup="tissue")
```

## Heatmap

```{r}
library("pheatmap")
ntd <- normTransform(dds2)
select <- order(rowMeans(counts(dds2,normalized=TRUE)),
                decreasing=TRUE)[1:20]
df <- as.data.frame(colData(dds2)[,c("tissue","subject")])

pheatmap(assay(ntd)[select,], cluster_rows=FALSE,
         cluster_cols=FALSE, annotation_col=df,
         fontsize_col=3)
```

## Tissue `boxplots` from the `dds` object
`Boxplots` from the `dds` object. Tissue specific boxplots showing logFC genes

```{r}
#load("gDDS2_SEtissuesRNAseqGE.RData")
```

```{r}
head(res)
res[1:10,]
```

If necessary load from here

```{r}
#load("gDDS2_SEtissuesRNAseqGE.RData")
```

```{r}
resOrdered[1:5,]
```

Select genes of interests:

```{r}
goi <- rownames(resOrdered)[1:9]
stopifnot(all(goi %in% names(dds)))
goi
```

```{r fat}
goiAD<-c("LINCADL", "LEP", "ADIPOQ", "PLIN1", "LIPE", "DEFB132", "PLIN4", "CSN1S1", "ADIPOQ-AS1")
```

```{r}
goiAdDdown <- c("PLAC4", "NR0B2", "CRISP2", "ITGB1BP1", "ITLN2", "TM4SF5")
```

```{r adrenal}
goiAdrenal <- c("CYP11B1", "CYP11B2", "HSD3B2", "CYP21A2", "TNXA", "MC2R", "TH", "ARHGAP36", "CYP17A1")
```

appendix

```{r}
goiAPP <- c("VIP", "IGHG4", "MMP10", "PI15", "GAL", "FPR2","CXCL5", "MADCAM1", "CXCR1")
```

```{r}
goiBL <- c("UPK2", "KRT13", "LINC02888", "FMO9P", "UPK1A", "PADI3", "IGHV1-58", "DHRS2", "CLEC3A")
```

```{r}
goiBM <- c("PRTN3", "AZU1", "DEFA4", "DEFA1", "DEFA1B", "ELANE", "DEFA3", "HBD", "RNASE3")
```

```{r}
goiCRTX <- c("OPALIN", "GFAP", "OLIG2", "NCAN", "SNCB", "MOG", "NEUROD2", "AMER2", "VSTM2B")
```

```{r}
goiCOL <- c("INSL5", "MS4A12", "BEST2", "GAL3ST2", "NOX1", "LYPD8", "NXPE1", "CEACAM7", "SI")
```

```{r}
goiDUO <- c("S100G", "TMPRSS15", "SI", "ADH4", "TREH", "ADA", "CDH17", "SLC15A1", "GBA3")
```

```{r}
goiENDO <- c("LINC01541", "MMP10", "MMP26", "LEFTY2", "PAEP", "ZCCHC12", "SCGB1D2", "TRH", "PGR")
```

```{r}
goiESO <- c("TMPRSS11B", "CRNN", "MUC21", "KRT6C", "KRT4", "SPRR3", "IL36A", "SPRR2A", "GBP6")
```

```{r}
goiFALL <- c("OVGP1", "FOXN3-AS3", "LDLRAD1", "SNTN", "STOML3", "ANKRD66", "TMEM212", "TUBA4B", "WDR38")
```

```{r}
goiGALL <- c("APCS", "FGF19", "CHST4", "MOGAT1", "UGT2B28", "UGT2B10", "CCKAR", "LINC02331", "LINC02159")
```

```{r}
goiHeart <- c("NPPB", "MYL7", "NPPA", "MYH6", "TNNI3", "TECRL", "MYBPC3", "ANKRD1", "LRRC10")
```

```{r}
goiKID <- c("SLC22A8", "UMOD", "SLC22A6", "SLC22A12", "SLC12A1", "TMEM174", "AQP2", "SLC34A1", "NPHS2")
```

```{r}
goiLIV <- c("AHSG", "F9", "CFHR2", "MBL2", "APOA2", "SERPINC1", "F2", "FGB", "C9")
```

```{r}
goiLUN <- c("SFTPA1", "SFTPC", "SFTPB", "SFTPA2", "CHIAP2", "SCGB1A1", "SCGB3A2", "NAPSA", "SFTPD")
```

```{r}
goiLYM <- c("LINC01991", "IL21", "PLA2G2D", "SERPINA9", "IGHV1-14", "TCL1A", "LINC02909", "AICDA", "RGS13")
```

```{r}
goiOV <- c("ECEL1", "WFIKKN2", "KLHDC8A", "MAG", "CRYGD", "ARX", "LEMD1-AS1", "SIGLEC16", "ANGPTL5")
```

```{r}
goiPAN <- c("CTRB2", "PNLIP", "CELA3A", "AMY2A", "CELA2A", "CELA3B", "PRSS1", "CPA1", "PNLIPRP1")
```

Placenta

```{r}
goiPL <- c("CSH1", "CSH2", "PSG1", "PSG2", "CSHL1", "PSG6", "PSG9", "PSG11", "GH2")
```

```{r}
goiPR <- c("TGM4", "KLK2", "KLK3", "KLK4", "PCAT4", "PCGEM1", "ACP3", "MSMB", "CHRNA2")
```

```{r}
goiREC <- c("FSIP1", "NOX1", "MUC12", "CDHR1", "B3GALT5-AS1", "LINC01752", "SATB2-AS1", "COXFA4L3", "SATB2")
```

```{r}
goiSG <- c("PRB1", "PRB4", "PRB3", "PRB2", "HTN3", "HTN1", "BPIFA2", "STATH", "PRH2")
```

```{r}
goiSKEL <- c("MYH1", "ACTN3", "MYBPC2", "IDI2", "MYH2", "MYL11", "TNNC2", "MYOZ1", "ATP2A1")
```

```{r}
goiSKIN <- c("FLG2", "KPLCE", "KRT2", "CASP14", "KRT77", "LORICRIN", "KRT1", "SERPINA12", "LCE2B")
```

```{r}
goiSI <- c("FABP6", "MLN", "CPO", "LINC02200", "TMPRSS15", "REG3A", "KCNJ13", "ITLN2", "SLC17A8")
```

```{r}
goiSMOO <- c("LINC00578", "TNC", "FAM83D", "MYLK", "ITGA11", "ACTA2", "TRPC3", "TAGLN", "TNFAIP8L3")
```

```{r}
goiSPL <- c("OR5AK4P", "OR5AK2", "CD5L", "FAM9C", "LINC02138", "SPIC", "ITGAD", "NOX5", "STAB2")
```

```{r}
goiSTO <- c("GKN1", "PGA4", "PGA3", "PGA5", "LIPF", "MUC5AC", "DAZ1", "GKN2", "TFF1")
```

```{r}
goiTE <- c("GAGE12E", "PRM2", "PRM1", "BOD1L2", "TNP1", "C16orf82", "TUBA3C", "AKAP4", "UBQLN3")
```

```{r}
goiTHYR <- c("TG", "RPL21P78", "FOXE1", "TPO", "PTCSC2", "TSHR", "PTCSC3", "SLC26A4-AS1", "OTOS")
```

```{r}
goiTON <- c("SPRR3", "PAX1", "MUC21", "LCE3A", "KRT13", "IL36G", "HEPHL1", "KRT24", "IGKV2-29")
```

Join and tidy

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```

```{r}
tcounts <- t(log2((counts(dds2[goiAdDdown, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiAdDdown)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```

```{r}
p1_9ad <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top adipose genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("AD", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```

```{r}
p1_9ad
```

```{r}
tcounts <- t(log2((counts(dds2[goiAdrenal, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>% gather(gene, expression, (ncol(.)-length(goiAdrenal)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```

```{r}
p1_9adr <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top adrenal genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "AG", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```

```{r}
p1_9adr
```



APP

```{r}
tcounts <- t(log2((counts(dds2[goiAPP, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiAPP)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9ap <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top appendix genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "AP", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9ap
```

BLADDER
goiBL

```{r}
tcounts <- t(log2((counts(dds2[goiBL, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiBL)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9bl <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top bladder genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "BL", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9bl
```

Bone Marrow
goiBM

```{r}
tcounts <- t(log2((counts(dds2[goiBM, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiBM)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9bm <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top bone marrow genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "BM", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9bm
```

Cortex
goiCRTX

```{r}
tcounts <- t(log2((counts(dds2[goiCRTX, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiCRTX)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9crtx <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top cortex genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "CRX", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9crtx
```


Colon
goiCOL

```{r}
tcounts <- t(log2((counts(dds2[goiCOL, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiCOL)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9col <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top colon genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "COL", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9col
```

Duodenum
goiDUO

```{r}
tcounts <- t(log2((counts(dds2[goiDUO, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiDUO)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9duo <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top duodenum genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "DUO", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9duo
```

Endometrium
goiENDO

```{r}
tcounts <- t(log2((counts(dds2[goiENDO, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiENDO)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9endo <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top endometrium genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "EM", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9endo
```

Oesophagus
goiESO

```{r}
tcounts <- t(log2((counts(dds2[goiESO, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiESO)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9eso <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top oesophagus genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "ES", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9eso
```

Gall bladder
goiGB

```{r}
tcounts <- t(log2((counts(dds2[goiGB, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiGB)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9gb <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top gall bladder genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "GB", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9gb
```

Heart
goiHeart

```{r}
tcounts <- t(log2((counts(dds2[goiHeart, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiHeart)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9heart <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top heart genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "H", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9heart
```

Kidney
goiKID

```{r}
tcounts <- t(log2((counts(dds2[goiKID, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiKID)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9kid <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top kidney genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "K", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9kid
```

Liver
goiLIV

```{r}
tcounts <- t(log2((counts(dds2[goiLIV, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiLIV)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9liv <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top Liver genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "LI", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9liv
```

Lungs
goiLUN

```{r}
tcounts <- t(log2((counts(dds2[goiLUN, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiLUN)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9LU <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top lung genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "LU", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9LU
```

Lymp node
goiLYM

```{r}
tcounts <- t(log2((counts(dds2[goiLYM, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiLYM)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9LN <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top lymph node genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "LN", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9LN
```

Ovaries

```{r}
tcounts <- t(log2((counts(dds2[goiOV, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>% gather(gene, expression, (ncol(.)-length(goiOV)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```

```{r}
p1_9ov <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top ovarian genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "OV", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```

```{r}
p1_9ov
```

Pancreas
goiPAN

```{r}
tcounts <- t(log2((counts(dds2[goiPAN, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiPAN)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9PAN <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top pancreas genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "PN", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9PAN
```

Placenta
goiPL

```{r}
tcounts <- t(log2((counts(dds2[goiPL, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiPL)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9PL <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top placenta genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "PL", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9PL
```

Prostate
goiPR

```{r}
tcounts <- t(log2((counts(dds2[goiPR, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiPR)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9PR <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top prostate genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "PR", "", "", "", "", "", "", ""))
```
```{r}
p1_9PR
```

Salivary gland
goiSG

```{r}
tcounts <- t(log2((counts(dds2[goiSG, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiSG)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9sg <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top salivary gland genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "SG", "", "", "", "", "", ""))
```
```{r}
p1_9sg
```

Small Intestine
goiSI

```{r}
tcounts <- t(log2((counts(dds2[goiSI, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiSI)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9si <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top small intestine genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "SI", "", "", "", ""))
```
```{r}
p1_9si
```

Skin
goiSKIN

```{r}
tcounts <- t(log2((counts(dds2[goiSKIN, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiSKIN)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9skin <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top skin genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "SK", "", "", "", "", ""))
```
```{r}
p1_9skin
```

Spleen
goiSPL

```{r}
tcounts <- t(log2((counts(dds2[goiSPL, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiSPL)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9spl <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top spleen genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "SP", "", "", ""))
```
```{r}
p1_9spl
```

Stomach
goiSTO

```{r}
tcounts <- t(log2((counts(dds2[goiSTO, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiSTO)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9sto <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top stomach genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "ST", "", ""))
```
```{r}
p1_9sto
```

Testis
goiTE

```{r}
tcounts <- t(log2((counts(dds2[goiTE, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiTE)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9te <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top testis genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "TE", ""))
```
```{r}
p1_9te
```
Thyroid
goiTHYR

```{r}
tcounts <- t(log2((counts(dds2[goiTHYR, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiTHYR)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9thyr <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top thyroid genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "TY"))
```
```{r}
p1_9thyr
```

# Session info

```{r sessionInfo}
sessionInfo()
```

