---
title: "TissueBoxplots"
author: "Sulev Koks"
date: "2026-07-17"
output: html_document
---

## Tissue `boxplots` from the `dds` object
`Boxplots` from the `dds` object. Tissue specific boxplots showing logFC genes

```{r}
#load("gDDS2_SEtissuesRNAseqGE.RData")
```

```{r}
head(res)
res[1:10,]
```

If necessary load from here

```{r}
#load("gDDS2_SEtissuesRNAseqGE.RData")
```

```{r}
resOrdered[1:5,]
```

Select genes of interests:

```{r}
goi <- rownames(resOrdered)[1:9]
stopifnot(all(goi %in% names(dds)))
goi
```

```{r fat}
goiAD<-c("LINCADL", "LEP", "ADIPOQ", "PLIN1", "LIPE", "DEFB132", "PLIN4", "CSN1S1", "ADIPOQ-AS1")
```

```{r adrenal}
goiAdrenal <- c("CYP11B1", "CYP11B2", "HSD3B2", "CYP21A2", "TNXA", "MC2R", "TH", "ARHGAP36", "CYP17A1")
```

appendix

```{r}
goiAPP <- c("VIP", "IGHG4", "MMP10", "PI15", "GAL", "FPR2","CXCL5", "MADCAM1", "CXCR1")
```

```{r}
goiBL <- c("UPK2", "KRT13", "LINC02888", "FMO9P", "UPK1A", "PADI3", "IGHV1-58", "DHRS2", "CLEC3A")
```

```{r}
goiBM <- c("PRTN3", "AZU1", "DEFA4", "DEFA1", "DEFA1B", "ELANE", "DEFA3", "HBD", "RNASE3")
```

```{r}
goiCRTX <- c("OPALIN", "GFAP", "OLIG2", "NCAN", "SNCB", "MOG", "NEUROD2", "AMER2", "VSTM2B")
```

```{r}
goiCOL <- c("INSL5", "MS4A12", "BEST2", "GAL3ST2", "NOX1", "LYPD8", "NXPE1", "CEACAM7", "SI")
```

```{r}
goiDUO <- c("S100G", "TMPRSS15", "SI", "ADH4", "TREH", "ADA", "CDH17", "SLC15A1", "GBA3")
```

```{r}
goiENDO <- c("LINC01541", "MMP10", "MMP26", "LEFTY2", "PAEP", "ZCCHC12", "SCGB1D2", "TRH", "PGR")
```

```{r}
goiESO <- c("TMPRSS11B", "CRNN", "MUC21", "KRT6C", "KRT4", "SPRR3", "IL36A", "SPRR2A", "GBP6")
```

```{r}
goiFALL <- c("OVGP1", "FOXN3-AS3", "LDLRAD1", "SNTN", "STOML3", "ANKRD66", "TMEM212", "TUBA4B", "WDR38")
```

```{r}
goiGALL <- c("APCS", "FGF19", "CHST4", "MOGAT1", "UGT2B28", "UGT2B10", "CCKAR", "LINC02331", "LINC02159")
```

```{r}
goiHeart <- c("NPPB", "MYL7", "NPPA", "MYH6", "TNNI3", "TECRL", "MYBPC3", "ANKRD1", "LRRC10")
```

```{r}
goiKID <- c("SLC22A8", "UMOD", "SLC22A6", "SLC22A12", "SLC12A1", "TMEM174", "AQP2", "SLC34A1", "NPHS2")
```

```{r}
goiLIV <- c("AHSG", "F9", "CFHR2", "MBL2", "APOA2", "SERPINC1", "F2", "FGB", "C9")
```

```{r}
goiLUN <- c("SFTPA1", "SFTPC", "SFTPB", "SFTPA2", "CHIAP2", "SCGB1A1", "SCGB3A2", "NAPSA", "SFTPD")
```

```{r}
goiLYM <- c("LINC01991", "IL21", "PLA2G2D", "SERPINA9", "IGHV1-14", "TCL1A", "LINC02909", "AICDA", "RGS13")
```

```{r}
goiOV <- c("ECEL1", "WFIKKN2", "KLHDC8A", "MAG", "CRYGD", "ARX", "LEMD1-AS1", "SIGLEC16", "ANGPTL5")
```

```{r}
goiPAN <- c("CTRB2", "PNLIP", "CELA3A", "AMY2A", "CELA2A", "CELA3B", "PRSS1", "CPA1", "PNLIPRP1")
```

Placenta

```{r}
goiPL <- c("CSH1", "CSH2", "PSG1", "PSG2", "CSHL1", "PSG6", "PSG9", "PSG11", "GH2")
```

```{r}
goiPR <- c("TGM4", "KLK2", "KLK3", "KLK4", "PCAT4", "PCGEM1", "ACP3", "MSMB", "CHRNA2")
```

```{r}
goiREC <- c("FSIP1", "NOX1", "MUC12", "CDHR1", "B3GALT5-AS1", "LINC01752", "SATB2-AS1", "COXFA4L3", "SATB2")
```

```{r}
goiSG <- c("PRB1", "PRB4", "PRB3", "PRB2", "HTN3", "HTN1", "BPIFA2", "STATH", "PRH2")
```

```{r}
goiSKEL <- c("MYH1", "ACTN3", "MYBPC2", "IDI2", "MYH2", "MYL11", "TNNC2", "MYOZ1", "ATP2A1")
```

```{r}
goiSKIN <- c("FLG2", "KPLCE", "KRT2", "CASP14", "KRT77", "LORICRIN", "KRT1", "SERPINA12", "LCE2B")
```

```{r}
goiSI <- c("FABP6", "MLN", "CPO", "LINC02200", "TMPRSS15", "REG3A", "KCNJ13", "ITLN2", "SLC17A8")
```

```{r}
goiSMOO <- c("LINC00578", "TNC", "FAM83D", "MYLK", "ITGA11", "ACTA2", "TRPC3", "TAGLN", "TNFAIP8L3")
```

```{r}
goiSPL <- c("OR5AK4P", "OR5AK2", "CD5L", "FAM9C", "LINC02138", "SPIC", "ITGAD", "NOX5", "STAB2")
```

```{r}
goiSTO <- c("GKN1", "PGA4", "PGA3", "PGA5", "LIPF", "MUC5AC", "DAZ1", "GKN2", "TFF1")
```

```{r}
goiTE <- c("GAGE12E", "PRM2", "PRM1", "BOD1L2", "TNP1", "C16orf82", "TUBA3C", "AKAP4", "UBQLN3")
```

```{r}
goiTHYR <- c("TG", "RPL21P78", "FOXE1", "TPO", "PTCSC2", "TSHR", "PTCSC3", "SLC26A4-AS1", "OTOS")
```

```{r}
goiTON <- c("SPRR3", "PAX1", "MUC21", "LCE3A", "KRT13", "IL36G", "HEPHL1", "KRT24", "IGKV2-29")
```

Join and tidy

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```

Adipose

```{r}
tcounts <- t(log2((counts(dds2[goiAD, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiAD)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```

```{r}
p1_9ad <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top adipose genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("AD", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```

```{r}
p1_9ad
```

Adrenal

```{r}
tcounts <- t(log2((counts(dds2[goiAdrenal, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>% gather(gene, expression, (ncol(.)-length(goiAdrenal)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```

```{r}
p1_9adr <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top adrenal genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "AG", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```

```{r}
p1_9adr
```

Appendix

```{r}
tcounts <- t(log2((counts(dds2[goiAPP, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiAPP)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9ap <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top appendix genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "AP", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9ap
```

BLADDER
goiBL

```{r}
tcounts <- t(log2((counts(dds2[goiBL, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiBL)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9bl <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top bladder genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "BL", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9bl
```

Bone Marrow
goiBM

```{r}
tcounts <- t(log2((counts(dds2[goiBM, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiBM)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9bm <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top bone marrow genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "BM", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9bm
```

Cortex
goiCRTX

```{r}
tcounts <- t(log2((counts(dds2[goiCRTX, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiCRTX)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9crtx <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top cortex genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "CRX", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9crtx
```

Colon
goiCOL

```{r}
tcounts <- t(log2((counts(dds2[goiCOL, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiCOL)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9col <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top colon genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "COL", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9col
```

Duodenum
goiDUO

```{r}
tcounts <- t(log2((counts(dds2[goiDUO, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiDUO)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9duo <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top duodenum genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "DUO", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9duo
```

Endometrium
goiENDO

```{r}
tcounts <- t(log2((counts(dds2[goiENDO, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiENDO)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9endo <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top endometrium genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "EM", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9endo
```

Oesophagus
goiESO

```{r}
tcounts <- t(log2((counts(dds2[goiESO, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiESO)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9eso <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top oesophagus genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "ES", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9eso
```

Fallopian Tube
goiFALL

```{r}
tcounts <- t(log2((counts(dds2[goiFALL, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiFALL)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9fall <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top fallopian tube genes") +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "FT", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9fall
```

Gall bladder
goiGALL

```{r}
tcounts <- t(log2((counts(dds2[goiGALL, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiGALL)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9gb <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top gall bladder genes") +
  theme(legend.position = "none") +
  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "GB", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9gb
```

Heart
goiHeart

```{r}
tcounts <- t(log2((counts(dds2[goiHeart, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiHeart)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9heart <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top heart genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "H", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9heart
```

Kidney
goiKID

```{r}
tcounts <- t(log2((counts(dds2[goiKID, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiKID)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9kid <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top kidney genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "K", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9kid
```

Liver
goiLIV

```{r}
tcounts <- t(log2((counts(dds2[goiLIV, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiLIV)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9liv <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top Liver genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "LI", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9liv
```

Lungs
goiLUN

```{r}
tcounts <- t(log2((counts(dds2[goiLUN, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiLUN)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9LU <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top lung genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "LU", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9LU
```

Lymp node
goiLYM

```{r}
tcounts <- t(log2((counts(dds2[goiLYM, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiLYM)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9LN <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top lymph node genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "LN", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9LN
```

Ovaries
goiOV

```{r}
tcounts <- t(log2((counts(dds2[goiOV, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>% gather(gene, expression, (ncol(.)-length(goiOV)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```

```{r}
p1_9ov <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top ovarian genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "OV", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```

```{r}
p1_9ov
```

Pancreas
goiPAN

```{r}
tcounts <- t(log2((counts(dds2[goiPAN, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiPAN)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9PAN <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top pancreas genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "PN", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9PAN
```

Placenta
goiPL

```{r}
tcounts <- t(log2((counts(dds2[goiPL, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiPL)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9PL <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top placenta genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "PL", "", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9PL
```

Prostate
goiPR

```{r}
tcounts <- t(log2((counts(dds2[goiPR, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiPR)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9PR <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top prostate genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "PR", "", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9PR
```

Rectum
goiREC

```{r}
tcounts <- t(log2((counts(dds2[goiREC, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiREC)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9REC <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top rectum genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "RE", "", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9REC
```

Salivary gland
goiSG

```{r}
tcounts <- t(log2((counts(dds2[goiSG, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiSG)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9sg <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top salivary gland genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "SG", "", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9sg
```

Skeletal muscle
goiSKEL

```{r}
tcounts <- t(log2((counts(dds2[goiSKEL, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiSKEL)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9skel <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top skeletal muscle genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "SM", "", "", "", "", "", "", "", ""))
```
```{r}
p1_9skel
```

Skin
goiSKIN

```{r}
tcounts <- t(log2((counts(dds2[goiSKIN, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiSKIN)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9skin <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top skin genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "SK", "", "", "", "", "", "", ""))
```
```{r}
p1_9skin
```

Small Intestine
goiSI

```{r}
tcounts <- t(log2((counts(dds2[goiSI, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiSI)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9si <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top small intestine genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "SI", "", "", "", "", "", ""))
```
```{r}
p1_9si
```

Smooth muscle
goiSMOO

```{r}
tcounts <- t(log2((counts(dds2[goiSMOO, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiSMOO)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9smoo <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top smooth muscle genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "SM", "", "", "", "", ""))
```
```{r}
p1_9smoo
```

Spleen
goiSPL

```{r}
tcounts <- t(log2((counts(dds2[goiSPL, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiSPL)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9spl <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top spleen genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "SP", "", "", "", ""))
```
```{r}
p1_9spl
```

Stomach
goiSTO

```{r}
tcounts <- t(log2((counts(dds2[goiSTO, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiSTO)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9sto <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top stomach genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "ST", "", "", ""))
```
```{r}
p1_9sto
```

Testis
goiTE

```{r}
tcounts <- t(log2((counts(dds2[goiTE, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiTE)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9te <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top testis genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "TE", "", ""))
```
```{r}
p1_9te
```

Thyroid
goiTHYR

```{r}
tcounts <- t(log2((counts(dds2[goiTHYR, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiTHYR)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9thyr <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top thyroid genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "TY", ""))
```
```{r}
p1_9thyr
```

Tonsil
goiTON 

```{r}
tcounts <- t(log2((counts(dds2[goiTON , ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiTON )+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```
```{r}
p1_9ton <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top tonsil genes") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "TO"))
```
```{r}
p1_9ton
```

Combined figures

```{r}
goiCOMB1 <- c("ADIPOQ", "MC2R", "GAL", "UPK2", "PRTN3", "GAL3ST2", "OPALIN", "S100G", "LINC01541")
```

Combined 1

``` {r}
tcounts <- t(log2((counts(dds2[goiCOMB1, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiCOMB1)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```

```{r}
p1_9comb1 <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top genes combined 1 ") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```

```{r}
p1_9comb1
```


```{r}
goiCOMB2 <- c("KRT6C", "OVGP1", "APCS", "NPPB", "SLC22A8", "F9", "SFTPA1", "LINC01991", "WFIKKN2")
```

Combined 2

``` {r}
tcounts <- t(log2((counts(dds2[goiCOMB2, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiCOMB2)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```

```{r}
p1_9comb2 <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top genes combined 2 ") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```

```{r}
p1_9comb2
```


```{r}
goiCOMB3 <- c("CTRB2", "CSH2", "TGM4", "FSIP1", "PRB1", "MYH1", "KPLCE", "FABP6", "LINC00578")
```

Combined 3

``` {r}
tcounts <- t(log2((counts(dds2[goiCOMB3, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiCOMB3)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```

```{r}
p1_9comb3 <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top genes combined 3 ") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```

```{r}
p1_9comb3
```

```{r}
goiCOMB4 <- c("OR5AK4P", "GKN1", "C16orf82", "TG", "SPRR3", "MMP10", "CCKAR", "IL36G", "IL21")
```

Combined 4

``` {r}
tcounts <- t(log2((counts(dds2[goiCOMB4, ], normalized=TRUE, replaced=FALSE)+.5))) %>%
  merge(colData(dds2), ., by="row.names") %>%
  gather(gene, expression, (ncol(.)-length(goiCOMB4)+1):ncol(.))
```

```{r}
tcounts %>% 
  select(Row.names, tissue, gene, expression) %>% head %>%  knitr::kable()
```

```{r}
p1_9comb4 <- ggplot(tcounts, aes(tissue, expression, fill=tissue)) + 
  geom_boxplot() + 
  facet_wrap(~gene, scales="free_y") + 
  labs(x="Tissues", 
       y="Expression (log normalised counts)", 
       fill="Tissues", 
       title="Top genes combined 4") + theme(legend.position = "none") +  scale_x_discrete(labels = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""))
```

```{r}
p1_9comb4
```




# Session info

```{r sessionInfo}
sessionInfo()
```
